Variable creation ObjectInAction

### 2020-06-29 Final_Manuscript.Rmd
updates about combining samples

Data from two different, but demographically equivalent, samples were combined to create the final analysis sample (*N =* `r nrow(clarksmith_women)`) used in this study. In the measures section that follows we refer to them as Sample 1 and Sample 2. Sample 1 (*N =* `r ns[3]`) is from a co-ed liberal arts college in the northeast US and Sample 2 (*N =* `r ns[4]`) is from a women’s liberal arts college in the northeast US.

@@

# Results
```{r create_r-references, warning=FALSE, message=FALSE}
#cite_r(file = "references.bib")
r_refs(file = "r-references.bib")
```

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.

```{r apim, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Basic actor-partner interdependence model (APIM) depiction."}
include_graphics("APIM_figure.png")
```

```{r 2016figure, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Path Analysis Model from Garcia et al. (2016) study with distinguishable dyads."}
include_graphics("2016_figure.jpg")
```

## Analysis Strategy
This study sought to replicate the results of @garcia2016objectification’s study, done with male-female pairs, which used a dyadic path analysis to detect whether partners’ objectification of one another affected state self-objectification (SSO). See Figure\ \@ref(fig:2016figure) for the results of the analysis from this previous study. We hope to investigate how the central effects found in the previous study relate to interactions between two women. Specifically, we are interested in testing the relationship between state-other objectification and SSO, and how SSO in turn, affecs feelings of inauthenticity during the interaction. In addition, we will also test if the effect of other-objectification in an interaction on SSO is only present for those women who are high in trait self-objectification, as in @garcia2016objectification. Further, we will investigate the realtionships between experiencing interaction inauthenticity and relationship agency, career aspirations, and cognitive performance.

@@

@@

@@

```{r}
#SSO
apim1 <- gls(howbody_avg_A ~ a2pSOO_A + a2pSOO_P + TSO_A + a2pSOO_P*TSO_A, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID),
                 data=clarksmith_women)

@@

summary(apim1)
```

```{r}
#authenticity
apim2 <- gls(authenticity_A ~ howbody_avg_A, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID),
                 data=clarksmith_women)

@@

summary(apim2.c)
```

```{r}
#cognitive performance
apim3 <- gls(trigram_score_A ~ authenticity_A, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID),
                 data=clarksmith_women)

@@

summary(apim3.c)
```

```{r}
#relationship agency
apim4 <- gls(relag_A ~ authenticity_A, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID),
                 data=clarksmith_women)

@@

summary(apim4.c)
```

```{r}
#career aspirations
apim5 <- gls(careerasp_A ~ authenticity_A, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID),
                 data=clarksmith_women)

@@

summary(apim5.c)
```

```{r semfigure, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Path Analysis Model with Estimates"}
include_graphics("SEMfigure.png")
```

```{r mlm, include=TRUE, results='asis'}
# fit_table <- xtable(parameterEstimates(fit))
# 
# fit_table <- fit_table %>%
#   filter(op=="~") %>%
#   mutate(lhs = ifelse(lhs == "howbody_avg_A", "Actor SSO",
#                       ifelse(lhs=="authenticity_A", "Actor Authenticity",
#                              ifelse(lhs=="howbody_avg_P", "Partner SSO",
#                                     ifelse(lhs=="authenticity_P", "Partner Authenticity",
#                                            ifelse(lhs=="relag_A", "Actor Rel. Agency",
#                                                   ifelse(lhs=="relag_P", "Partner Rel. Agency",
#                                                          ifelse(lhs=="careerasp_A", "Actor Career Aspirations",
#                                                                 ifelse(lhs=="careerasp_P", "Partner Career Aspirations",
#                                                                        ifelse(lhs=="trigram_score_A", "Actor Cog. Performance",
#                                                                               ifelse(lhs=="trigram_score_P", "Partner Cog. Performance", NA)))))))))),
#          rhs = ifelse(rhs=="TSO_A", "Actor TSO",
#                       ifelse(rhs=="a2pSOO_A", "Actor Obj. of Partner",
#                              ifelse(rhs=="a2pSOO_P", "Partner Obj. of Actor",
#                                     ifelse(rhs=="TSO_A_SOO_P", "Actor TSO x Partner Obj.",
#                                            ifelse(rhs == "howbody_avg_A", "Actor SSO",
#                                                   ifelse(rhs=="howbody_avg_P", "Partner SSO",
#                                                          ifelse(rhs=="TSO_P", "Partner TSO",
#                                                                 ifelse(rhs=="TSO_P_SOO_A", "Partner TSO x Actor Obj.",
#                                                                        ifelse(rhs=="authenticity_A", "Actor Authenticity",
#                                                                               ifelse(rhs=="authenticity_P", "Partner Authenticity", NA))))))))))) %>%
#   select(lhs, op, rhs, est, se, z, pvalue) %>%
#   #taking out partner-partner estimates
#   slice(1:5,11:13)
# 
# colnames(fit_table) <- c("Path", "", "", "Estimate", "SE", "z-value", "p-value")
# 
# apa_table(fit_table, caption = "Estimates from final Path Analysis Model", font_size = "small")
```

@@

>>>>

Data from two different, but demographically equivalent, samples were combined to create the final analysis sample (*N =* `r nrow(clarksmith_women)`) used in this study. In the measures section that follows we refer to them as Sample 1 and Sample 2. Sample 1 (*N =* `r ns[3]`) is from a co-ed liberal arts college in the northeast US and Sample 2 (*N =* `r ns[4]`) is from a women’s liberal arts college in the northeast US. The results section contains more detail about equivalence analyses to support the decision to combine these two samples.

@@

# Results
```{r create_r-references, warning=FALSE, message=FALSE}
#cite_r(file = "references.bib")
r_refs(file = "r-references.bib")
```
## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.
```{r apim, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Basic actor-partner interdependence model (APIM) depiction."}
include_graphics("APIM_figure.png")
```
```{r 2016figure, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Path Analysis Model from Garcia et al. (2016) study with distinguishable dyads."}
include_graphics("2016_figure.jpg")
```
## Analysis Strategy
This study sought to replicate the results of @garcia2016objectification’s study, done with male-female pairs, which used a dyadic path analysis to detect whether partners’ objectification of one another affected state self-objectification (SSO). See Figure\ \@ref(fig:2016figure) for the results of the analysis from this previous study. We hope to investigate how the central effects found in the previous study relate to interactions between two women. Specifically, we are interested in testing the relationship between state-other objectification and SSO, and how SSO in turn, affecs feelings of inauthenticity during the interaction. In addition, we will also test if the effect of other-objectification in an interaction on SSO is only present for those women who are high in trait self-objectification, as in @garcia2016objectification. Further, we will investigate the realtionships between experiencing interaction inauthenticity and relationship agency, career aspirations, and cognitive performance.

@@

Before moving to the main analyses, we discuss statistical equivalence test that provide support for combining Sample 1 and Sample 2 in one analysis sample. The online supplemental material contains the main analyses separated by samples.

@@

### Combining Samples

The correaltions between study variables is similar across samples. The realibialities for the study scales were also equivalent. (Note that the two samples were two small to conduct formal measurement equivalence tests for scales.) There are no statistically significant differences between samples in demographics including age, STATS, and ethnicity, STATS. 

@@

#SSO
apim1 <- gls(howbody_avg_A ~ a2pSOO_A + a2pSOO_P + TSO_A + a2pSOO_P*TSO_A, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID),
                 data=clarksmith_women)

@@

summary(apim1)
```
```{r}
#authenticity
apim2 <- gls(authenticity_A ~ howbody_avg_A, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID),
                 data=clarksmith_women)

@@

summary(apim2.c)
```
```{r}
#cognitive performance
apim3 <- gls(trigram_score_A ~ authenticity_A, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID),
                 data=clarksmith_women)

@@

summary(apim3.c)
```
```{r}
#relationship agency
apim4 <- gls(relag_A ~ authenticity_A, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID),
                 data=clarksmith_women)

@@

summary(apim4.c)
```
```{r}
#career aspirations
apim5 <- gls(careerasp_A ~ authenticity_A, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID),
                 data=clarksmith_women)

@@

summary(apim5.c)
```
```{r semfigure, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Path Analysis Model with Estimates"}
include_graphics("SEMfigure.png")
```
```{r mlm, include=TRUE, results='asis'}
# fit_table <- xtable(parameterEstimates(fit))
# 
# fit_table <- fit_table %>%
#   filter(op=="~") %>%
#   mutate(lhs = ifelse(lhs == "howbody_avg_A", "Actor SSO",
#                       ifelse(lhs=="authenticity_A", "Actor Authenticity",
#                              ifelse(lhs=="howbody_avg_P", "Partner SSO",
#                                     ifelse(lhs=="authenticity_P", "Partner Authenticity",
#                                            ifelse(lhs=="relag_A", "Actor Rel. Agency",
#                                                   ifelse(lhs=="relag_P", "Partner Rel. Agency",
#                                                          ifelse(lhs=="careerasp_A", "Actor Career Aspirations",
#                                                                 ifelse(lhs=="careerasp_P", "Partner Career Aspirations",
#                                                                        ifelse(lhs=="trigram_score_A", "Actor Cog. Performance",
#                                                                               ifelse(lhs=="trigram_score_P", "Partner Cog. Performance", NA)))))))))),
#          rhs = ifelse(rhs=="TSO_A", "Actor TSO",
#                       ifelse(rhs=="a2pSOO_A", "Actor Obj. of Partner",
#                              ifelse(rhs=="a2pSOO_P", "Partner Obj. of Actor",
#                                     ifelse(rhs=="TSO_A_SOO_P", "Actor TSO x Partner Obj.",
#                                            ifelse(rhs == "howbody_avg_A", "Actor SSO",
#                                                   ifelse(rhs=="howbody_avg_P", "Partner SSO",
#                                                          ifelse(rhs=="TSO_P", "Partner TSO",
#                                                                 ifelse(rhs=="TSO_P_SOO_A", "Partner TSO x Actor Obj.",
#                                                                        ifelse(rhs=="authenticity_A", "Actor Authenticity",
#                                                                               ifelse(rhs=="authenticity_P", "Partner Authenticity", NA))))))))))) %>%
#   select(lhs, op, rhs, est, se, z, pvalue) %>%
#   #taking out partner-partner estimates
#   slice(1:5,11:13)
# 
# colnames(fit_table) <- c("Path", "", "", "Estimate", "SE", "z-value", "p-value")
# 
# apa_table(fit_table, caption = "Estimates from final Path Analysis Model", font_size = "small")
```

@@

The results were similar for analyses conducted on Sample 1 and Sample 2 individually. See the online supplemental material for more detail on these analyses.
